### 2022-05-06 docs/submission/manuscript.Rmd
init

authornote: |
  \vspace{-0.5cm}
  \noindent \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183} \newline
  \noindent \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
  \noindent \addORCIDlink{Joshua G.A. Cashaback}{0000-0002-8642-6648} \newline
  \noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
  \noindent Data and code: https://github.com/cartermaclab/expt_sc-feedback-characteristics \vspace{2ex} \newline
  \noindent \textbf{Corresponding authors:} Michael J. Carter (michaelcarter@mcmaster.ca) and Laura St. Germain (stgerml@mcmaster.ca).

@@

keywords          : "Self-controlled, Knowledge of results, OPTIMAL theory, Retention"
#wordcount         : "2978 for Introduction, Results, and Discussion"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "doc, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
 # - \pagewiselinenumbers
  - \raggedbottom

  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
---

@@

\vspace{4ex}

<!-- \vspace{2ex} -->

\newpage

@@

@@

\vspace{2.5ex}

# Funding

This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University. LSG was supported by an NSERC Postgraduate Scholarship. JGAC was supported by an NIH U45GM104941 grant. AW and AP were supported by NSERC Undergraduate Student Research Awards.

# Conflicts of interest/Competing interests

None.

# Availability of data, materials, and code

Can be accessed here: https://github.com/cartermaclab/expt_sc-feedback-characteristics.

# Authors' contributions using CRediT

Laura St. Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization. Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing. Andrew Poskus served as a lead for investigation - performed experiment and served in a supporting role for writing- original draft preparation and writing - review and editing. Allison Williams served as a lead for investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Olena Leshchyshen contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Sherry Feldman contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Joshua G.A. Cashaback contributed equally to conceptualization,  methodology, writing - original  draft preparation, and writing - review and editing. Michael J. Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.

>>>>

authornote: |
  \vspace{-0.5cm}
  \noindent \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183} \newline
  \noindent \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
  \noindent \addORCIDlink{Joshua G.A. Cashaback}{0000-0002-8642-6648} \newline
  \noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

  \noindent Data and code: https://github.com/cartermaclab/expt_sc-feedback-characteristics

  \noindent \textbf{Corresponding authors:} Michael J. Carter (michaelcarter@mcmaster.ca) or Laura St. Germain (stgerml@mcmaster.ca)

@@

keywords          : "Self-controlled, Knowledge of results, OPTIMAL theory, Retention"
wordcount         : "2978 for Introduction, Results, and Discussion"

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "man, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
  - \pagewiselinenumbers
  - \raggedbottom

  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
---

@@

@@

\vspace{2ex}

@@

\vspace{10ex}

# Declarations

\noindent
**Funding.** &nbsp;This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University. LSG was supported by an NSERC Postgraduate Scholarship. JGAC was supported by an NIH U45GM104941 grant. AW and AP were supported by NSERC Undergraduate Student Research Awards.

\noindent
**Conflicts of interest/Competing interests.** &nbsp;None.

\noindent
**Ethics approval.** &nbsp;This project was approved and conducted in accordance with the approval of the McMaster University Research Ethics Board.

\noindent
**Consent to participate.** &nbsp;All participants gave informed consent.

\noindent
**Consent for publication.** &nbsp;All authors approve the manuscript.

\noindent
**Availability of data, materials, and code.** &nbsp;Can be accessed here: https://github.com/cartermaclab/expt_sc-feedback-characteristics.

\noindent
**Authors' contributions using CRediT.** &nbsp;Laura St. Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization. Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing. Andrew Poskus served as a lead for investigation - performed experiment and served in a supporting role for writing- original draft preparation and writing - review and editing. Allison Williams served as a lead for investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Olena Leshchyshen contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Sherry Feldman contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Joshua G.A. Cashaback contributed equally to conceptualization,  methodology, writing - original  draft preparation, and writing - review and editing. Michael J. Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.
